Semi-parametric generalized linear model for correlated binary data

### 2022-03-11 nuweb/SPGLM.tex
Improve robustness of variance calculation

\begin{flushleft} \small\label{scrap13}\raggedright\small
\NWtarget{nuweb11b}{} $\langle\,${\itshape Calculate standard errors}\nobreak\ {\footnotesize {11b}}$\,\rangle\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@  data_object_mod <- list(model_matrix = mm, resp=Y, n=rowSums(Y), @\\
\mbox{}\verb@                          weights = weights, offset = offset, maxN = N, @\\
\mbox{}\verb@                          spt = spt, hyper_probs = hp)@\\
\mbox{}\verb@  ll <- function(x){@\\
\mbox{}\verb@    spglm_loglik(beta=x[1:p], f0 = exp(x[-(1:p)]), data_object=data_object_mod, link=link)@\\
\mbox{}\verb@  }@\\
\mbox{}\verb@@\\
\mbox{}\verb@  hess <- numDeriv::hessian(func=ll,  x=c(betas, log(referencef0)))@\\
\mbox{}\verb@  hess_idx <- c(1:p, p+spt+1) # betas and f0 elements with non-zero real support@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # revert to unlogged f0@\\
\mbox{}\verb@  grad <- c(rep(1, p), 1/referencef0[spt+1])@\\
\mbox{}\verb@  hess1 <- diag(grad) %*% hess[hess_idx, hess_idx] %*% diag(grad)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # create bordered hessian@\\
\mbox{}\verb@  border1 <- c(rep(0, p), rep(1, length(spt)))  # gradient of sum-to-one constraint@\\
\mbox{}\verb@  border2 <- c(rep(0, p), spt)          # gradient of fixed-mean constraint@\\
\mbox{}\verb@  bhess <- rbind(cbind(hess1, border1, border2), c(border1,0,0), c(border2,0,0))@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # calculate variance-covariance matrix@\\
\mbox{}\verb@  bvc <- tryCatch(solve(-bhess), error = function(e)NULL)@\\
\mbox{}\verb@  # bvc <- solve(-bhess)@\\
\mbox{}\verb@  if (!is.null(bvc)){@\\
\mbox{}\verb@    # remove border and set to 0 for zero-support values@\\
\mbox{}\verb@    vc <- matrix(0, nrow=p+N+1, ncol=p+N+1)@\\
\mbox{}\verb@    vc[hess_idx, hess_idx] <- bvc[1:(p+length(spt)), 1:(p+length(spt))]     @\\
\mbox{}\verb@  } else {@\\
\mbox{}\verb@    vc <- matrix(NA, nrow=p+N+1, ncol=p+N+1)@\\
\mbox{}\verb@  }@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtMacroRefIn\ \NWlink{nuweb7}{7}.

>>>>

\begin{flushleft} \small\label{scrap13}\raggedright\small
\NWtarget{nuweb11b}{} $\langle\,${\itshape Calculate standard errors}\nobreak\ {\footnotesize {11b}}$\,\rangle\equiv$
\vspace{-1ex}
\begin{list}{}{} \item
\mbox{}\verb@@\\
\mbox{}\verb@  data_object_mod <- list(model_matrix = mm, resp=Y, n=rowSums(Y), @\\
\mbox{}\verb@                          weights = weights, offset = offset, maxN = N, @\\
\mbox{}\verb@                          spt = spt, hyper_probs = hp)@\\
\mbox{}\verb@  ll <- function(x){@\\
\mbox{}\verb@    spglm_loglik(beta=x[1:p], f0 = exp(x[-(1:p)]), data_object=data_object_mod, link=link)@\\
\mbox{}\verb@  }@\\
\mbox{}\verb@@\\
\mbox{}\verb@  hess <- numDeriv::hessian(func=ll,  x=c(betas, log(referencef0)))@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # determine non-degenerate support@\\
\mbox{}\verb@  hess_spt <- which(referencef0 > sqrt(.Machine$double.eps))@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  hess_idx <- c(1:p, p+hess_spt) # betas and f0 elements with non-zero real support@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # revert to unlogged f0@\\
\mbox{}\verb@  grad <- c(rep(1, p), 1/referencef0[hess_spt])@\\
\mbox{}\verb@  hess1 <- diag(grad) %*% hess[hess_idx, hess_idx] %*% diag(grad)@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # create bordered hessian@\\
\mbox{}\verb@  border1 <- c(rep(0, p), rep(1, length(hess_spt)))  # gradient of sum-to-one constraint@\\
\mbox{}\verb@  border2 <- c(rep(0, p), hess_spt-1)          # gradient of fixed-mean constraint@\\
\mbox{}\verb@  bhess <- rbind(cbind(hess1, border1, border2), c(border1,0,0), c(border2,0,0))@\\
\mbox{}\verb@  @\\
\mbox{}\verb@  # calculate variance-covariance matrix@\\
\mbox{}\verb@  bvc <- tryCatch(solve(-bhess), error = function(e)NULL)@\\
\mbox{}\verb@  # bvc <- solve(-bhess)@\\
\mbox{}\verb@  if (!is.null(bvc)){@\\
\mbox{}\verb@    # remove border and set to 0 for zero-support values@\\
\mbox{}\verb@    vc <- matrix(0, nrow=p+N+1, ncol=p+N+1)@\\
\mbox{}\verb@    vc[hess_idx, hess_idx] <- bvc[1:(p+length(hess_spt)), 1:(p+length(hess_spt))]     @\\
\mbox{}\verb@  } else {@\\
\mbox{}\verb@    vc <- matrix(NA, nrow=p+N+1, ncol=p+N+1)@\\
\mbox{}\verb@  }@\\
\mbox{}\verb@@{\NWsep}
\end{list}
\vspace{-1.5ex}
\footnotesize
\begin{list}{}{\setlength{\itemsep}{-\parsep}\setlength{\itemindent}{-\leftmargin}}
\item \NWtxtMacroRefIn\ \NWlink{nuweb7}{7}.
